---
title: "Intro_to_RMarkdown"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Italic Text

*Poa* or *Poa*

# Michigan Native Grasses

1.  Sorgastrum
2.  Calamagrostis
3.  Andropogon

This is a cool website [mfield](https://mfield.umich.edu)

| Grass         | Height | Flavor |
|---------------|--------|--------|
| Sorgastrum    | 2 m    |        |
| Calamagrostis | 2.5 m  |        |
| Andropogon    | 2.25 m |        |

: Grass tastiness

```{r}
library(tidyverse)
library(readr)
```
## Introduction

* read in and reference data source(s)

```{r read-data, message=FALSE}
BGChem <- read_csv("BGchem2008data.csv")

BGChem
```

## Analysis

* calc basic summary stats
 - mean NO3
 - mean NO2
 - mean NH4
 - mean P
```{r}

nitrate <- mean(BGChem$NO3)
nitrite <- mean(BGChem$NO2)
amm <- mean(BGChem$NH4)
phos <- mean(BGChem$P)

```

* calc mean redfield ratio
```{r}
red <- (nitrate + nitrite + amm)/phos
```

We calculated the redfield ratio to be `r round(red, 2)`

* plot redfield ratio

```{r, echo= FALSE}
plot (BGChem$P, BGChem$NO2 + BGChem$NO3 + BGChem$NH4)
```

